Title Goes Here

### 2020-04-13 analysis/paper/paper.Rmd
commit before update my R...

Principal component analysis
```{r}
library(ggbiplot)

@@

@@

xx_pca2 <- 
df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

fviz_pca_var(xx_pca2, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

@@

PCA with corrplot package to understand the individual variables
```{r}
library(factoextra) #http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/112-pca-principal-component-analysis-essentials/

fviz_pca_var(PCA, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

>>>>

Principal component analysis

Principal Component Analysis is a technique to extract relevant information from a multivariate dataset and to express this information as a set of few new variables called principal components or dimensions [@cascalheira2018use].

In archaeology, PCA has been often used for~

We applied PCA to our dataset to identify correlations between variables that would represent the existence of patterns in the points, which could possilby be translated into more ~ , in addition to correlation analysis.

```{r}
library(ggbiplot)

@@

Contribution of variables for each of first two PCA demensions
```{r}
PC1_v <- fviz_contrib(xx_pca, choice = "var", axes = 1, top = 7)
PC2_v <- fviz_contrib(xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(PC1_v, PC2_v, nrow =1)

@@

# Color variables by the continuous variable
fviz_pca_var(xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

@@
